Rapid response of mesophyll conductance to light availability allows shade leaves to take advantage of sunflecks

### 2015-11-23 manuscript/manuscript_wtc3.Rmd
comments MT

\
Photosynthesis is also limited by the ability to supply water to the upper canopy. Ultimately, the ability of a trees hydraulic architecture to supply water to foliage across increasing pathlengths affects productivity and survival [@sellin2008effects]. Using a two-leaf model, Peltoniemi et al. [-@peltoniemi2012co] theorizes that optimal N distribution will be proportional to light distribution only if leaf K is also optimally distributed. In this study, variation in leaf N distribution and A rates were not associated with subsequent changes in leaf K between sun and shade leaves. As both sun and shade leaves were acclimated to their local light environment this sub-optimal distribution of water supply has the potential to diminish the C return for the whole canopy.

>>>>

\
Photosynthesis is also limited by the ability to supply water to the upper canopy. Ultimately, the ability of a trees hydraulic architecture to supply water to foliage across increasing pathlengths affects productivity and survival [@sellin2008effects]. Using a two-leaf model, Peltoniemi et al. [-@peltoniemi2012co] theorizes that optimal N distribution will be proportional to light distribution only if leaf K is also optimally distributed. In this study, variation in leaf N distribution and A rates were not associated with subsequent changes in leaf K between sun and shade leaves. As these trees were kept well watered, it appears that water supply was adequate and likely non-limiting to both sun and shade leaves.
